Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-28 manuscript/ERL_global_C_review.Rmd
fixed results in Data coverage section

idx_fluxes <- ForC_biome_averages$n.areas >= 7 & ForC_biome_averages$variable.type %in% "flux"
idx_stocks <- ForC_biome_averages$n.areas >= 7 & ForC_biome_averages$variable.type %in% "stock"

n_fluxes_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_fluxes])
n_stocks_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_stocks])
```

@@

Of the `r nrow(ForC_measurements)` records in *ForC* v3.0, `r n_records` met the criteria for inclusion in this study (Fig. 1).
These records were distributed across `r n_plots_tot` plots in `r n_areas_tot` distinct geographic areas.
Of the 23 flux and 11 stock variables mapped in these diagrams, *ForC* contained mature forest estimates from $\ge$ 7 distinct geographic areas for `r n_fluxes_with_ge7_areas[["Tropical broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Tropical broadleaf MATURE"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate broadleaf MATURE"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate conifer MATURE"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge7_areas[["Boreal conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Boreal conifer MATURE"]]` stocks in boreal forests.
For regrowth forests (<100 yrs), *ForC* contained estimates from $\ge$ 7 distinct geographic areas for `r n_fluxes_with_ge7_areas[["Tropical broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge7_areas[["Tropical broadleaf YOUNG"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate broadleaf YOUNG"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate conifer YOUNG"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate conifer YOUNG"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge7_areas[["Boreal conifer YOUNG"]]` fluxes and `r n_stocks_with_ge7_areas[["Boreal conifer YOUNG"]]` stocks in boreal forests.
**([issue 29](https://github.com/forc-db/ERL-review/issues/29#issuecomment-699633801))**

>>>>

idx_fluxes7 <- ForC_biome_averages$n.areas >= 7 & ForC_biome_averages$variable.type %in% "flux"
idx_stocks7 <- ForC_biome_averages$n.areas >= 7 & ForC_biome_averages$variable.type %in% "stock"
idx_fluxes3 <- ForC_biome_averages$n.areas >= 3 & ForC_biome_averages$variable.type %in% "flux"
idx_stocks3 <- ForC_biome_averages$n.areas >= 3 & ForC_biome_averages$variable.type %in% "stock"

n_fluxes_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_fluxes7])  
n_stocks_with_ge7_areas <- table(ForC_biome_averages$Biome[idx_stocks7])  
n_fluxes_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_fluxes3])  
n_stocks_with_ge3_areas <- table(ForC_biome_averages$Biome[idx_stocks3])  
```

@@

Of the `r nrow(ForC_measurements)` records in *ForC* v3.0, `r n_records` met our strict criteria for inclusion in this study (Fig. 1).
These records were distributed across `r n_plots_tot` plots in `r n_areas_tot` distinct geographic areas.
Of the 23 flux and 11 stock variables mapped in these diagrams, *ForC* contained sufficient mature forest data for inclusion in our statistical analyses (*i.e.*, records from $\ge$ 7 distinct geographic areas) for `r n_fluxes_with_ge7_areas[["Tropical broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Tropical broadleaf MATURE"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate broadleaf MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate broadleaf MATURE"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge7_areas[["Temperate conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Temperate conifer MATURE"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge7_areas[["Boreal conifer MATURE"]]` fluxes and `r n_stocks_with_ge7_areas[["Boreal conifer MATURE"]]` stocks in boreal forests.
For regrowth forests (<100 yrs), *ForC* contained sufficient data for inclusion in our statistical analyses (*i.e.*, records from $\ge$ **3** distinct geographic areas) for `r n_fluxes_with_ge3_areas[["Tropical broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Tropical broadleaf YOUNG"]]` stocks in tropical broadleaf forests, `r n_fluxes_with_ge3_areas[["Temperate broadleaf YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Temperate broadleaf YOUNG"]]` stocks in temperate broadleaf forests, `r n_fluxes_with_ge3_areas[["Temperate conifer YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Temperate conifer YOUNG"]]` stocks in temperate conifer forests, and `r n_fluxes_with_ge3_areas[["Boreal conifer YOUNG"]]` fluxes and `r n_stocks_with_ge3_areas[["Boreal conifer YOUNG"]]` stocks in boreal forests.
